Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-11-03 VMCAI-revised-version/final.tex

\begin{proof}
Let $V$ be a reset-VASS, $q_0({\bf 0})$ an initial state of $V$,
and $q_f({\bf 0})$ a terminal state of $V$.
We build $V'$ from $V$ by additionnally allowing from any control-state to get back to 
$q_0({\bf 0})$
by a transition reseting every counter and
changing the control-state to $q_0$. Remark that the set of states 
reachable from $q_0({\bf 0})$ is the same in $V'$ and in $V$.
Then $q_f({\bf 0})$ is reachable from $q_0({\bf 0})$ in $V$
iff $q_f({\bf 0})$ is reachable from every state in $V'$,
which corresponds to {\sc Resilience} in $V'$ for $\Safe =  \{ q_f({\bf 0}) \}$.
Indeed, if $q_f({\bf 0})$ is reachable from $q_0({\bf 0})$ in $V$,
then, since $q_0({\bf 0})$ is reachable from every state in $V'$,
$q_f({\bf 0})$ is reachable from every state in $V'$.
In the other direction, if $q_f({\bf 0})$ is reachable from every state in $V'$,
then in particular $q_f({\bf 0})$ is reachable from $q_0({\bf 0})$ in $V'$,
hence $q_f({\bf 0})$ is reachable from $q_0({\bf 0})$ in $V$.
\end{proof}

>>>>

\begin{proof}
Let $V$ be a reset-VASS, $q_0({\bf 0})$ an initial state of $V$,
and $q_f({\bf 0})$ a terminal state of $V$.
We build $V'$ from $V$ by additionnally allowing from any control-state to get back to 
$q_0({\bf 0})$
by a transition reseting every counter and
changing the control-state to $q_0$. Remark that the set of states 
reachable from $q_0({\bf 0})$ is the same in $V'$ and in $V$.
Then $q_f({\bf 0})$ is reachable from $q_0({\bf 0})$ in $V$
iff $q_f({\bf 0})$ is reachable from every state in $V'$,
which corresponds to {\sc Resilience} in $V'$ for $\Safe =  \{ q_f({\bf 0}) \}$.
Indeed, if $q_f({\bf 0})$ is reachable from $q_0({\bf 0})$ in $V$,
then, since $q_0({\bf 0})$ is reachable from every state in $V'$,
$q_f({\bf 0})$ is reachable from every state in $V'$.
In the other direction, if $q_f({\bf 0})$ is reachable from every state in $V'$,
then in particular $q_f({\bf 0})$ is reachable from $q_0({\bf 0})$ in $V'$,
hence $q_f({\bf 0})$ is reachable from $q_0({\bf 0})$ in $V$.\qed
\end{proof}
